\documentclass[margin,line]{resume}
\usepackage[hidelinks]{hyperref}

\begin{document}
\name{\Large Prakash Kumar}
\begin{resume}
    \section{\mysidestyle Contact\\Information}

    Phone: (248) 882-2897       \hfill Github: \url{https://www.github.com/pkash16} \\
    \noindent Email: prakashk@umich.edu  \vspace{0mm}\\\vspace{-4.5mm}

    \section{\mysidestyle Education}

    \textbf{University of Michigan}, Ann Arbor, MI \vspace{2mm}\\\vspace{1mm}%
    \textsl{B.S., Computer Engineering, Minor in Multidisciplinary Design Program} \hfill \textbf{Sep 2016 -- May 2020}\\
   	\emph{Current Cumulative GPA: 3.53}
   	
   	
   	\section{\mysidestyle Coursework}
   	\begin{itemize}
   		\item EECS 215,216,280,281,270: Signals and Systems, Circuits, Data Structures and Algorithms, Digital Logic Design. 
   		\item PAT 201/202: Introduction to Computer Music/Audio. Training at the Duderstadt Audio Studio.
   	 	\item Next Semester: EECS 352, 373: Digital Signal Processing, Embedded Systems
   	\end{itemize}

    \section{\mysidestyle Professional\\Experience}
    
    
    \textbf{Radiation Oncology Flat Panel Imager Group}, Ann Arbor, MI \vspace{2mm}\\\vspace{1mm}%
    \textsl{Research Assistant, Electronics Lab} \hfill \textbf{Jan 2018 -- Dec 2018}
    \begin{itemize}
    	\item Wrote Systemverilog to program FPGA boards to interface with poly-silicon flat panel X-ray arrays, using UART and SPI communications to help aid research team in debugging X-ray communications
    	\item Soldered components onto the lab's custom boards, and tested functionality using multimeters and oscilliscopes
    \end{itemize}
    
    \textbf{Multidisciplinary Design Program, MAESTRO}, Ann Arbor, MI \vspace{2mm}\\\vspace{1mm}%
    \textsl{Algorithms Subteam} \hfill \textbf{Jan 2018 -- Dec 2018}
    \begin{itemize}
    	\item Designed signal processing algorithms to interpret music conducting gestures using an Inertial Measurement Unit, acceleration and gyroscope data.
    	\item Used Matlab and Python/Pandas to write real-time data analysis and transforms on sampled data to provide audio feedback to conducting students at the School of Music
    \end{itemize}
    
    
    \textbf{Robotics Toolkit Workshop}, Ann Arbor, MI \vspace{2mm}\\\vspace{1mm}%
    \textsl{Pilot Student} \hfill \textbf{Sep 2017 -- Dec 2017}
    \begin{itemize}
    	\item Design, built, and tested an autonomous line-following robot using a beaglebone, IMUs, a custom line-sensing PCB module, and motors as a pilot student testing new program for graduate students.
    \end{itemize}
    	
	\textbf{HealthPals}, San Francisco Bay Area, CA \vspace{2mm}\\\vspace{1mm}%
	\textsl{Software Engineering Intern} \hfill \textbf{May 2017 -- August 2017}
	\begin{itemize}
		\item Full Stack liaison between the frontend and backend engineering teams in the development of the CLINT product(developed in python and react.js), designed to give value based decisions to clinicians at the point of care.
		\item Analyzed several thousand anonymous patient records while providing useful insights on patients' risk for cardiovascular disease by writing a Population Dashboard using javascript, python/pandas, and seaborn.
	\end{itemize}




\iffalse

\textbf{Underwater ROV Design/Build/Test}, Ann Arbor, MI \vspace{2mm}\\\vspace{1mm}%
\textsl{Student/Hardware Engineer} \hfill \textbf{Jan 2017 -- May 2017}
\begin{itemize}
	\item Built an underwater ROV to compete in a competition for the Engineering 100 class at the University of Michigan.
	\item Used Arduinos and RF transmitters/receivers to build a remote control and bluetooth camera system allowed complete control and vision of the underwater ROV.
	

\end{itemize}
\fi
	\textbf{Internet of Things Home Automation}, Northville, MI \vspace{2mm}\\\vspace{1mm}%
	\textsl{Side Project} \hfill \textbf{Aug 2015 -- Jun 2017}
	\begin{itemize}
		\item Developed a RESTful API for my personal garage using Twilio, Node.js and a Raspberry Pi that controlled the garage via web application, text message or android application for easy access to the house.
	\end{itemize}

\iffalse
    \textbf{Mobile Application Development}, Northville, MI \vspace{2mm}\\\vspace{1mm}%
    \textsl{Side Project} \hfill \textbf{Jan 2014 -- Aug 2014}
    \begin{itemize}
    	\item 	Developed and launched "Psychoblocks", a video game for the android platform using Java and the Libgdx cross­platform library. Used Google Play Game Services to connect data to Google Servers.
    \end{itemize}
	\fi
	\iffalse
    \textbf{Blind Sensor Navigation}, Northville, MI \vspace{2mm}\\\vspace{1mm}%
	\textsl{Side Project} \hfill \textbf{Nov 2013 -- Jun 2014}
	\begin{itemize}
		\item Built a device running on an ATMega328p micro­controller that helps a visually impaired individual navigate around their surroundings. Received 1st place IEEE award at the 2014 Science and Engineering Fair of Metro Detroit. 
	\end{itemize}
	\fi

   \section{\mysidestyle Leadership}
   	Music Director of Maize Mirchi A Cappella, a South Asian interest a cappella group on campus. President of the Bursley Hall Council, managed funds, sponsored local organizations and led community events for the benefit of residents.
   	
   	
   \vspace{-2mm}

    \section{\mysidestyle Skills}

    \emph{Languages:} SystemVerilog, Python, Javascript, CSS, C,  C++, C\#, Unity, Bash, \LaTeX, Java, Swift \\
    \emph{Other Technology:}  Arduino, Raspberry Pi, Soldering, DipTrace(PCB Design), Redis, SQL, MongoDB, Vivado, Circuit Analysis, MultiSim, Oscilliscopes, Logic Pro X, Ableton Live, Max MSP
\end{resume}
\end{document}
